Group 5 Report

### 2022-08-02 Report/Group 5 report.Rmd
Commen on names.
Added Innsamlingskontrollen. Added CARE net income/loss graph. Changing text on Fundraising ROI.

@@

## Creating df------------------------------------------------------------------
kreftforeningen <- read_proff("Data/Kreftforeningen.html", "2002", "2021")

@@

<!--# En webcrawler er en bot -->

@@

<!-- # Legger inn tre grafer som viser manglende data i Proffs årsregnskap-->

@@

```{r CEO, echo=FALSE, fig.align='center', fig.asp=0.618, fig.cap="CEO compensation data for the Norwegian Cancer Society from Proff.no"}
kreftforeningen |>
  # preparing for pivoting
  select(
    year, lederlonn, leder_annen_godtgjorelse
  ) |>
  # Compensation in ordinary numbers
  mutate(
    lederlonn = lederlonn * 1000,
    leder_annen_godtgjorelse = leder_annen_godtgjorelse * 1000
  ) |>
  # renaming for the purposes of the plot
  rename(
    Year = year,
    Salary = lederlonn,
    `Other compensation` = leder_annen_godtgjorelse
  ) |>
  # pivoting to join the two values to use fill
  pivot_longer(c(Salary, `Other compensation`), names_to = "Compensation") |>
  ggplot(aes(Year, value, fill = Compensation)) +
  geom_col() +
  # using currency scale function to add correct currency code or ?
  scale_y_continuous(labels = scales::label_dollar(prefix = "NOK ")) +
  # pretty colours
  scale_fill_met_d("Hokusai2", direction = -1) +
  labs(
    x = "", y = ""
  ) +
  theme_light() +
  theme(legend.position = "bottom")
```

@@

- **Fundraising ROI**:
  - A basic measure of the return on investment of direct fundraising expenses:

@@

This KPI is not a true measure of fundraising ROI, as it only includes (as we understand OPX's data) the direct fundraising expenses, and does not include major indirect expenses such as salary costs.

>>>>

<!--# Vi burde vel ha navnene våre, siden rapporten skal lastes opp på Inspera?-->
<!--# Legg til et sted: The Norwegian Control Committee for Fundraising (Innsamlingskontrollen) also has some very basic financial data and information available about selected charitable organisations.-->

@@

## Creating dfs-----------------------------------------------------------------
kreftforeningen <- read_proff("Data/Kreftforeningen.html", "2002", "2021")
care <- read_proff("Data/CARENorge2010_2021.html", "2010", "2021")

@@

@@

<!-- # Legger inn fire grafer som viser manglende data i Proffs årsregnskap-->

@@

```{r CEO, echo=FALSE, fig.align='center', fig.asp=0.618, fig.cap="CEO compensation data for the Norwegian Cancer Society from Proff.no"}
kreftforeningen |>
  # preparing for pivoting
  select(
    year, lederlonn, leder_annen_godtgjorelse
  ) |>
  # Compensation in ordinary numbers
  mutate(
    lederlonn = lederlonn * 1000,
    leder_annen_godtgjorelse = leder_annen_godtgjorelse * 1000
  ) |>
  # renaming for the purposes of the plot
  rename(
    Year = year,
    Salary = lederlonn,
    `Other compensation` = leder_annen_godtgjorelse
  ) |>
  # pivoting to join the two values to use fill
  pivot_longer(c(Salary, `Other compensation`), names_to = "Compensation") |>
  ggplot(aes(Year, value, fill = Compensation)) +
  geom_col() +
  # using currency scale function to add correct currency code or ?
  scale_y_continuous(labels = scales::label_dollar(prefix = "NOK ")) +
  # pretty colours
  scale_fill_met_d("Hokusai2", direction = -1) +
  labs(
    x = "", y = ""
  ) +
  theme_light() +
  theme(legend.position = "top")
```

```{r care_arsresultat, echo=FALSE, fig.align='center', fig.asp=0.5, fig.cap="Net income/loss (in NOK 1,000) data for CARE Norway from Proff.no"}
care |>
  rename(
    Year = year,
    `Net income` = arsresultat,
    `Net positive` = annual_profit
  ) |>
  ggplot(aes(Year, `Net income`, fill = `Net positive`)) +
  geom_col() +
  scale_y_continuous(labels = scales::label_dollar(prefix = "NOK ")) +
  scale_fill_green(kreftforeningen$annual_profit) +
  labs(
    x = "", y = ""
  ) +
  theme_light() +
  theme(legend.position = "none")
```

@@

- **Fundraising ROI**:
  - A basic measure of the return on investment of fundraising expenses:

@@

Whether this is a true measure of fundraising ROI depends on how the underlying data have been calculated -- e.g. if they include salary costs, etc.
